---
title: "NutritionMortality"
author: "Theodoros Papakonstantinou"
date: "2024-03-11"
output: html_document
---

```{r setup, include=FALSE}
rm(list=ls())
knitr::opts_chunk$set(echo = TRUE)
source("studygraph.R")
```

Read mortality data

```{r readData, echo=T}
ACM_5_with_networks <- read_excel("data/mortality/ACM-5%-networks-final-with-subgroups-solution179.xlsx")

#Insert variance
studyTable <- ACM_5_with_networks %>% 
  filter(!is.na(effect)) %>% 
  mutate(var = se^2)
```

```{r treatmentOrders ,echo=F}
treatment_order <- read_excel("treatment_order.xlsx", 
                              skip = 1)
```

Get all studies

```{r studies ,echo=T}
studyIds <- unique(studyTable$id)
```

There are `r length(studyIds)` studies

We now check studies for variance and effect inconsistency.

```{r studyReport, echo=T}
studyIds <- unique(studyTable$id)
errorstudies <- c()
warnmess <- c()
studyInconsistency <- data.frame()
studyGraphs <- lapply(studyIds, function(stid){
  res <- {}
  tryCatch({
    stgr <- fullGraph(stid, studyTable ,rand=F)
    res <- stgr
  },error = function(cond){
    # print(c("error in study",stid))
    errorstudies <<- c(errorstudies,stid)
    # message(conditionMessage(cond))
  })
  return(res)
})
SGs <- Filter(function(g){!is.null(g)},studyGraphs)
incgs <- Filter(function(g){g$inc & g$pvalue < 0.90},SGs)
lapply(incgs, function(g){plotDiffs(g)})
```

### Analysis and forest plots

For each network, the network plot and the forest plots of logRRs using the random effects model are shown. 
All results and plots are in the **results** directory.
The R objects are saved as `.rds` files

```{r Analysis}
report <- lapply(1:7,function(netid){
    print(paste("Network ", netid, sep=""))
    pairwiseReport(studyTable, SGs, netid, "mortality")
    netReport(studyTable, SGs, netid, "mortality")
})
```

### Subgroup for RoB
```{r subgroup ROB Analysis}
report <- lapply(1:7,function(netid){
    print(paste("Network ", netid, sep=""))
    netReport(studyTable, SGs, netid, "mortality", subgroup="RoB_subg")
})
```

### Subgroup for Location
```{r subgroup Location Analysis}
report <- lapply(1:7,function(netid){
    print(paste("Network ", netid, sep=""))
    netReport(studyTable, SGs, netid, "mortality", subgroup="location_subg")
})
```

### Subgroup for multiple Diet
```{r subgroup multidiet Analysis}
report <- lapply(1:7,function(netid){
    print(paste("Network ", netid, sep=""))
    netReport(studyTable, SGs, netid, "mortality", subgroup="multiplediet_subg")
})
```

## Read the Results - Example Network 2

To access the network's 2 results you just load
`results/mortality/network/mortalitynet2.rds`
either by the command indicated or by opening the file with rstudio
```{R results_net_2example}
mortalityallnet2 <- readRDS("results/mortality/network/all/mortalityallnet2.rds")
```
Get the order of treatments 
```{R results_net_2examplea}
mortalityallnet2$netobj$trts
```
Define a custom treatment order for the forestplot
```{R results_net_2exampleb}
trtsOrder <- c("PUFA","PRO", "SFA", "TFA","CHO", "MUFA"  )
```

We have to rerun netmeta
```{R results_net_2examplenetmeta}
net2 <- netmeta( TE=TE, seTE=seTE
               , treat1=treat1, treat2=treat2
               , studlab=studlab
               , data=mortalityallnet2$netobj$data
               , sm="RR"
               , seq=trtsOrder
               )
```

Get the league table
```{R results_net_2exampleLeague}
nl2 <- netleague(net2)
print(nl2$random)
```
And the forest plots will follow the order defined
```{R results_net_2forest}
 forest(net2
       , label.right="Network 2"
       , smlab=paste("RR Mortality")
       )
```
