---
title: "Nutrition Type 2 Diabetes"
author: "Theodoros Papakonstantinou"
date: "2024-02-29"
output: html_document
---

```{r setup, include=FALSE}
rm(list=ls())
knitr::opts_chunk$set(echo = TRUE)
source("studygraph.R")
```

Read t2d data

```{r readData, echo=T}
t2dData <- read_excel("data/t2d/T2D-with-networks-HGI_LGI.xlsx")

#Insert variance
studyTable <- t2dData %>% 
  filter(!is.na(effect)) %>% 
  mutate(var = se^2)
```

Get all studies

```{r studies ,echo=T}
studyIds <- unique(studyTable$id)
```

There are `r length(studyIds)` studies

We now check studies for variance and effect inconsistency.

```{r studyReport, echo=T}
studyIds <- unique(studyTable$id)
errorstudies <- c()
warnmess <- c()
studyInconsistency <- data.frame()
studyGraphs <- lapply(studyIds, function(stid){
  res <- {}
  tryCatch({
    stgr <- fullGraph(stid, studyTable ,rand=F)
    res <- stgr
  },error = function(cond){
    # print(c("error in study",stid))
    errorstudies <<- c(errorstudies,stid)
    # message(conditionMessage(cond))
  })
  return(res)
})
SGs <- Filter(function(g){!is.null(g)},studyGraphs)
incgs <- Filter(function(g){g$inc & g$pvalue < 0.90},SGs)
lapply(incgs, function(g){plotDiffs(g)})
```

### Analysis and forest plots

For each network, the network plot and the forest plots of logRRs using the random effects model are shown. 
All results and plots are in the **results** directory.
The R objects are saved as `.rds` files

```{r Analysis}
report <- lapply(1:7,function(netid){
    print(paste("Network ", netid, sep=""))
    pairwiseReport(studyTable, SGs, netid, "t2d")
    netReport(studyTable, SGs, netid, "t2d")
})
```


### Subgroup for sex
```{r subgroup sex Analysis}
report <- lapply(1:7,function(netid){
    print(paste("Network ", netid, sep=""))
    netReport(studyTable, SGs, netid, "t2d", subgroup="sex")
})
```

## Read the Results - Example Network 2

To access the network's 2 results you just load
`results/t2d/network/t2dnet2.rds`
either by the command indicated or by opening the file with rstudio

```{R results_net_2example}
t2dallnet2 <- readRDS("results/t2d/network/all/t2dallnet2.rds")
print(t2dallnet2)
```